
# Clicker Questions

to go along with <br>

<b><a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R, 3rd edition</a></b> by Baumer, Kaplan, and Horton

<b><a href = "https://www.statlearning.com/" target = "_blank">Introduction to Statistical Learning with Applications in R</a></b> by James, Witten, Hastie, and Tibshirani


<!-- the two formats are html and revealjs -->


```{=html}
<style>
.reveal ol ol {
   list-style-type: lower-alpha;
}
</style>
```


```{r}
#| echo: false
#| message: false
#| warning: false

# figure options
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
  fig.width = 10, fig.asp = 0.618, out.width = "90%",
  fig.retina = 3, dpi = 300, fig.align = "center"
)

library(tidyverse)

# Make sure to put a space before and after every slide break "---"

```

---

1. The reason to take random samples is:[^1]
   (a) to make cause and effect conclusions 
   (b) to get as many variables as possible
   (c) it's easier to collect a large dataset
   (d) so that the data are a good representation of the population
   (e) I have no idea why one would take a random sample

[^1]: d. so that the data are a good representation of the population

---

2. The reason to allocate/assign explanatory variables is:[^2]
   (a) to make cause and effect conclusions 
   (b) to get as many variables as possible
   (c) it's easier to collect a large dataset
   (d) so that the data are a good representation of the population
   (e) I have no idea what you mean by "allocate/assign" (or "explanatory variable" for that matter)

[^2]: a. to make cause and effect conclusions

---

3. Approximately how big is a tweet?[^3]
   (a) 0.01Kb
   (b) 0.1Kb
   (c) 1Kb
   (d) 100Kb
   (e) 1000Kb = 1Mb

[^3]: b. about 0.1Kb.  Turns out that 3.5 billion tweets * 0.1Kb = 350Gb (0.35 Tb).  My laptop is pretty good, and it has 36 Gb of memory (RAM) and 4 Tb of storage.  It would not be able to work with 3.5 billion tweets.

---

4. $R^2$ measures:[^4]
   (a) the proportion of variability in vote margin as explained by tweet share.
   (b) the proportion of variability in tweet share as explained by vote margin.
   (c) how appropriate the linear part of the linear model is.
   (d) whether or not particular variables should be included in the model.

[^4]: a. the proportion of variability in vote margin as explained by tweet share.

---

5. R / R Studio / Quarto[^5]
    (a) all good
    (b) started, progress is slow and steady
    (c) started, very stuck
    (d) haven’t started yet
    (e) what do you mean by "R"?

[^5]: wherever you are, make sure you are communicating with me when you have questions!

---

6. Git / GitHub[^6]
    (a) all good
    (b) started, progress is slow and steady
    (c) started, very stuck
    (d) haven’t started yet
    (e) what do you mean by "Git"?

[^6]: wherever you are, make sure you are communicating with me when you have questions!

---

7. Which of the following includes talking to the remote version of GitHub?[^7]
    (a) changing your name (updating the YAML)
    (b) committing the file(s)
    (c) pushing the file(s)
    (d) some of the above
    (e) all of the above
    
[^7]: d. pushing the file(s)

---

8. What is the error?[^8]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup2 <-- "Hello to you!"
```

[^8]: a. poor assignment operator

---

9. What is the error?[^9]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
3shup <-  "Hello to you!"
```

[^9]: d. invalid object name

---

10. What is the error?[^10]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup4 <-  "Hello to you!
```

[^10]: b. unmatched quotes

---

11. What is the error?[^11]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup5 <-  date()
```

[^11]: e. no mistake

---

12. What is the error?[^12]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup6 <-  sqrt 10
```

[^12]: c. improper syntax for a function argument

---

13. Do you keep a calendar / schedule / planner?[^13]
     (a) Yes
     (b) No
     
[^13]: a. I mean, the right answer has to be Yes, right!??!

---

14.  Do you keep a calendar / schedule / planner?  If you answered "Yes" ...[^14]
     (a)	Yes, on Google Calendar
     (b)	Yes, on Calendar for macOS
     (c)	Yes, on Outlook for Windows
     (d)	Yes, in some other app
     (e)	Yes, by hand


[^14]: no right answer here!

---

15. Where should I put things I've created for the HW (e.g., data, .ics file, etc.)[^15]
    (a) Upload into remote GitHub directory
    (b) In the local folder which also has the R project
    (c) In my Downloads
    (d) Somewhere on my Desktop
    (e) In my Home directory
    
[^15]: b. In the local folder which also has the R project.  It could be on the Desktop or the Home directory, but it must be in the same place as the R project. Do **not** upload files to the remote GitHub directory or you will find yourself with two different copies of the files.

---

16. The goal of making a figure is...[^16]
     (a)  To draw attention to your work.
     (b) To facilitate comparisons.
     (c) To provide as much information as possible.

[^16]: Yes! All the responses are reasons to make a figure.

---

17. A good reason to make a particular choice of a graph is:[^17]
     (a) Because the journal / field has particular expectations for how the data are presented.
     (b) Because some variables naturally fit better on some graphs (e.g., numbers on scatter plots).
     (c) Because that graphic displays the message you want as optimally as possible.

[^17]: c. Because that graphic displays the message you want as optimally as possible.

---

18. Why are the points orange?[^18]
     (a) R translates "navy" into orange.
     (b) color must be specified in `geom_point()`
     (c) color must be specified **outside** the `aes()` function
     (d) the default plot color is orange
     
:::: {.columns}

::: {.column width="35%"}
```{r}
#| echo: false
library(mosaic)
data(Births78)
ggplot(data = Births78, 
       aes(x = date, y = births, color = "navy")) + 
  geom_point() +          
  ggtitle("US Births in 1978")
```
:::

::: {.column width="65%"}
```{r}
#| eval: false
#| echo: true
ggplot(data = Births78, 
       aes(x = date, y = births, color = "navy")) + 
  geom_point() +          
  ggtitle("US Births in 1978")
```
:::

::::

[^18]: c. color must be specified **outside** the `aes()` function

---

19. Why are the dots blue and the lines colored?[^19]
     (a) dot color is given as "navy", line color is given as `wday`.
     (b) both colors are specified in the `ggplot()` function.
     (c) dot coloring takes precedence over line coloring.
     (d) line coloring takes precedence over dot coloring.
     
```{r}
#| echo: false
#| out-width: 60%
library(mosaic)
data(Births78)
ggplot(data = Births78, 
       aes(x = date, y = births)) + 
  geom_line(aes(color = wday)) +       
  geom_point(color = "navy") +          
  ggtitle("US Births in 1978")
```
     
[^19]: a. dot color is specified as "navy", line color is specified as `wday`.

---

20. Setting vs. Mapping.  If I want information to be passed to all data points (not variable):[^20]
     (a) map the information inside the `aes()` function.
     (b) set the information outside the `aes()` function
     
[^20]: b. set the information outside the `aes()` function

---

21. The Snow figure was most successful at:[^21]
     (a) making the data stand out
     (b) facilitating comparison
     (c) putting the work in context
     (d) simplifying the story

[^21]: answers may vary. I'd say c. putting the work in context.  Others might say b. facilitating comparison or d. simplifying the story.  However, I don't think a correct answer is a. making the data stand out.

---

22. The Challenger figure(s) was(were) least successful at:[^22]
    (a) making the data stand out
    (b) facilitating comparison
    (c) putting the work in context
    (d) simplifying the story

[^22]: a. making the data stand out

---

23. The biggest difference between Snow and the Challenger was:[^23]
    (a)	The **amount** of information portrayed.
    (b)	One was better at displaying **cause**.
    (c)	One showed the relevant **comparison** better.
    (d)	One was more **artistic**.

[^23]: c. One showed the relevant **comparison** better.

---
 
24. Caffeine and Calories.  What was the biggest concern over the average value axes?[^24]
     (a) It isn’t at the origin.
     (b) They should have used all the data possible to find averages.
     (c) There wasn’t a random sample.
     (d) There wasn’t a label explaining why the axes were where they were.
     
[^24]: a. It isn’t at the origin. in combination with d. There wasn’t a label explaining why the axes were where they were.  The story associated with the average value axes is not clear to the reader.

---


