
# Clicker Questions

to go along with <br>

<b><a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R, 3rd edition</a></b> by Baumer, Kaplan, and Horton

<b><a href = "https://www.statlearning.com/" target = "_blank">Introduction to Statistical Learning with Applications in R</a></b> by James, Witten, Hastie, and Tibshirani


<!-- the two formats are html and revealjs -->


```{=html}
<style>
.reveal ol ol {
   list-style-type: lower-alpha;
}
</style>
```


```{r}
#| echo: false
#| message: false
#| warning: false

# figure options
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
  fig.width = 10, fig.asp = 0.618, out.width = "90%",
  fig.retina = 3, dpi = 300, fig.align = "center"
)

library(tidyverse)

# Make sure to put a space before and after every slide break "---"

```

---

1. The reason to take random samples is:[^1]
   (a) to make cause and effect conclusions 
   (b) to get as many variables as possible
   (c) it's easier to collect a large dataset
   (d) so that the data are a good representation of the population
   (e) I have no idea why one would take a random sample

[^1]: d. so that the data are a good representation of the population

---

2. The reason to allocate/assign explanatory variables is:[^2]
   (a) to make cause and effect conclusions 
   (b) to get as many variables as possible
   (c) it's easier to collect a large dataset
   (d) so that the data are a good representation of the population
   (e) I have no idea what you mean by "allocate/assign" (or "explanatory variable" for that matter)

[^2]: a. to make cause and effect conclusions

---

3. Approximately how big is a tweet?[^3]
   (a) 0.01Kb
   (b) 0.1Kb
   (c) 1Kb
   (d) 100Kb
   (e) 1000Kb = 1Mb

[^3]: b. about 0.1Kb.  Turns out that 3.5 billion tweets * 0.1Kb = 350Gb (0.35 Tb).  My laptop is pretty good, and it has 36 Gb of memory (RAM) and 4 Tb of storage.  It would not be able to work with 3.5 billion tweets.

---

4. $R^2$ measures:[^4]
   (a) the proportion of variability in vote margin as explained by tweet share.
   (b) the proportion of variability in tweet share as explained by vote margin.
   (c) how appropriate the linear part of the linear model is.
   (d) whether or not particular variables should be included in the model.

[^4]: a. the proportion of variability in vote margin as explained by tweet share.

---

5. R / R Studio / Quarto[^5]
    (a) all good
    (b) started, progress is slow and steady
    (c) started, very stuck
    (d) haven’t started yet
    (e) what do you mean by "R"?

[^5]: wherever you are, make sure you are communicating with me when you have questions!

---

6. Git / GitHub[^6]
    (a) all good
    (b) started, progress is slow and steady
    (c) started, very stuck
    (d) haven’t started yet
    (e) what do you mean by "Git"?

[^6]: wherever you are, make sure you are communicating with me when you have questions!

---

7. Which of the following includes talking to GitHub?[^7]
    (a) changing your name (updating the YAML)
    (b) committing the file(s)
    (c) pushing the file(s)
    (d) some of the above
    (e) all of the above
    
[^7]: d. some of the above (b. committing the file(s) and c. pushing the file(s))

---

8. What is the error?[^8]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup2 <-- "Hello to you!"
```

[^8]: a. poor assignment operator

---

9. What is the error?[^9]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
3shup <-  "Hello to you!"
```

[^9]: d. invalid object name

---

10. What is the error?[^10]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup4 <-  "Hello to you!
```

[^10]: b. unmatched quotes

---

11. What is the error?[^11]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup5 <-  date()
```

[^11]: e. no mistake

---

12. What is the error?[^12]
    (a) poor assignment operator
    (b) unmatched quotes
    (c) improper syntax for function argument
    (d) invalid object name
    (e) no mistake

```{r}
#| eval: false
#| echo: true
shup6 <-  sqrt 10
```

[^12]: c. improper syntax for a function argument

---

13. Do you keep a calendar / schedule / planner?[^13]
     (a) Yes
     (b) No
     
[^13]: a. I mean, the right answer has to be Yes, right!??!

---

14.  Do you keep a calendar / schedule / planner?  If you answered "Yes" ...[^14]
     (a)	Yes, on Google Calendar
     (b)	Yes, on Calendar for macOS
     (c)	Yes, on Outlook for Windows
     (d)	Yes, in some other app
     (e)	Yes, by hand


[^14]: no right answer here!

---



