---
title: "Schedule"
description: |
  Schedule for Math 154, Computational Statistics, Fall 2025
execute: 
  message: false
  warning: false
---

<!-- Note to self:  this broke when i upgraded the gt package above 0.11.0 (to 0.11.1).  not sure why!  didn't like the function: gt::fmt_markdown(columns = everything())  

require(remotes)
install_version("gt", version = "0.11.0")
-->

```{r}
#| echo: false 
library(tidyverse)
```

Here's your roadmap for the semester!
Each week, follow the general process outlined below:

- Enjoy the readings <i class="fas fa-book-open"></i>  

- Attend class, review slides <i class="fas fa-desktop" target="_blank"></i> for anything you missed on the agenda  

-   Homework assignments are found at the <a href = "https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> GitHub course organization</a>.  Due dates are provided on each assignment (roughly every other week).  See the <a href = "https://m154-comp-stats.netlify.app/github">course GitHub page</a> for more information on how to find, complete, and submit assignments.

- Examine the reflection questions <i class="fas fa-lightbulb"></i> which are provided in the <a href = "https://m154-comp-stats.netlify.app/daily" target = "_blank">daily sections</a>.

- Recognize and contemplate the ethics considerations <i class="fas fa-balance-scale"></i> which are provided in the <a href = "https://m154-comp-stats.netlify.app/daily" target = "_blank">daily sections</a>.


```{r echo = FALSE}
schedule <- tribble(
  ~`week`, ~topic, ~`due dates`, ~`reading`,
  "8.25.25", '<a href="posts/2025-08-25-getting-started/"><i class="fas fa-desktop" target="_blank"></i> starting with R + RStudio + Git</a> <br> <a href="posts/2025-08-27-dataviz/"><i class="fas fa-desktop" target="_blank"></i> data viz</a>',
  ' ',
  '<a href = "https://happygitwithr.com/" target = "_blank"><i class="fas fa-book-open"></i> happygitwithR</a>',

 "9.1.25", '<a href="posts/2025-09-03-wrangling/"><i class="fas fa-desktop" target="_blank"></i> wrangling</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 1</a> - due 9.3',
  ' ',
  
 "9.8.25", '<a href="posts/2025-09-08-simulating/"><i class="fas fa-desktop" target="_blank"></i> simulating</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 2</a> - due 9.10 <br> <i class="fa-regular fa-circle-question"></i> Quiz 1 (wrangling + ggplot) 9.10',
  ' ',
  
   "9.15.25", '<a href="posts/2025-09-08-simulating/"><i class="fas fa-desktop" target="_blank"></i> simulating</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 3</a> - due 9.17',
  ' ',

   "9.22.25", '<a href="posts/2025-09-22-permutation/"><i class="fas fa-desktop" target="_blank"></i> permutation tests</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 4</a> - due 9.24 <br> <i class="fa-regular fa-circle-question"></i> Quiz 2 (simulating) 9.24',
  ' ',

  "9.29.25", '<a href="posts/2025-09-22-permutation/"><i class="fas fa-desktop" target="_blank"></i> permutation tests</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 5</a> - due 10.1',
  ' ',

  "10.6.25", '<a href="posts/2025-10-01-bootstrap/"><i class="fas fa-desktop" target="_blank"></i> bootstrapping</a>',
  '<i class="fa-regular fa-circle-question"></i> Quiz 3 (permutation tests) 10.8',
  ' ',

  "10.15.25", '<a href="posts/2025-10-01-bootstrap/"><i class="fas fa-desktop" target="_blank"></i> bootstrapping</a>',
  ' ',
  ' ',
 
  '<font color = "#114B5F"><b>10.17.25</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><i class="fa-solid fa-chart-column"></i> <b>Initial Project Proposal due</b></font></a>', 'to Canvas <br> (Friday)',
  ' ',

 
 "10.20.25", '<a href="posts/2025-10-20-recipes"><i class="fas fa-desktop" target="_blank"></i> recipes + knn</a> <br>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 6</a> - due 10.20 <b>MONDAY!</b> <br> <i class="fa-regular fa-circle-question"></i> Quiz 4 (bootstrapping) 10.22',
  ' ',


  "10.27.25", '<a href="posts/2025-10-27-trees"><i class="fas fa-desktop" target="_blank"></i> trees + bagging</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 7</a> - due 10.29',
  ' ',

   '<font color = "#114B5F"><b>10.31.25</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"> <i class="fa-solid fa-chart-column"></i> <b>Final Project Proposal due</b></font></a>', 'to GitHub',
  ' ',

 "11.3.25", '<a href="posts/2025-11-03-rf"><i class="fas fa-desktop" target="_blank"></i> Random Forests</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 8</a> - due 11.5',
  ' ',

"11.10.25", '<a href="https://m154-comp-stats.netlify.app/posts/2025-11-10-svm/"><i class="fas fa-desktop" target="_blank"></i> support vector machines</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 9</a> - due 11.12 <br> <i class="fa-regular fa-circle-question"></i> Quiz 5 11.12 (knn + trees + forests)',
  ' ',

  '<font color = "#114B5F"><b>11.12.25</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><i class="fa-solid fa-chart-column"></i> <b>Project Update</b></font></a>', 'to GitHub',
  ' ',

"11.17.25", '<a href="https://m154-comp-stats.netlify.app/posts/2025-11-17-cluster/"><i class="fas fa-desktop" target="_blank"></i> clustering</a>',
  ' ',
  ' ',

 "11.24.25", '<a href="https://m154-comp-stats.netlify.app/posts/2025-11-17-cluster/"><i class="fas fa-desktop" target="_blank"></i> clustering</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 10</a> - due 11.26',
  ' ',

 "12.1.25", '<a href="https://m154-comp-stats.netlify.app/posts/2025-12-01-lda/"><i class="fas fa-desktop" target="_blank"></i> latent Dirichlet allocation +  extensions</a>',
  '<a href="https://github.com/orgs/ST47S-CompStats-Fall2025/repositories" target = "_blank"><i class="fas fa-code"></i> HW 11</a> - due 12.3.25 <br> <i class="fa-regular fa-circle-question"></i> Quiz 6 (SVM + clustering) 12.3',
  ' ',

 '<font color = "#114B5F"><b>12.5.25 + 12.08.25</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><i class="fa-solid fa-chart-column"></i> <b>Group Presentations</b></font></a>', 'in class, 2-5pm',
  ' ',

  '<font color = "#114B5F"><b>12.08.25</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><i class="fa-solid fa-chart-column"></i> <b>Final write-up</b></font></a>', 'to GitHub',' '
)
```


```{r}
#| echo: false
#| column: page
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(week ~ pct(10),
                 everything() ~ pct(30))
```



