---
title: "Schedule"
description: |
  Schedule for Math 154, Computational Statistics, Fall 2021
execute: 
  message: false
  warning: false
---


```{r}
#| echo: false 
library(tidyverse)
```

Here's your roadmap for the semester!
Each week, follow the general process outlined below:

- Enjoy the readings <i class="fas fa-book-open"></i>  

- Attend class, review slides <i class="fas fa-desktop" target="_blank"></i> for anything you missed on the agenda  

- Complete the assignment (see Sakai messages for HW link)  

- Discuss the reflection questions <i class="fas fa-lightbulb" target="_blank"></i> and ethics considerations <i class="fas fa-balance-scale"></i> with your classmates, mentor, and professor  


-   Homework assignments are found at the <a href = "https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">GitHub course organization</a>.  Due dates are provided on each assignment (roughly every other week).  See the <a href = "https://m154-comp-stats.netlify.app/github">course GitHub page</a> for more information on how to find, complete, and submit assignments.


```{r echo = FALSE}
schedule <- tribble(
  ~`date`, ~topic, ~`due dates`, 
  "8.26.24", '<a href="posts/2024-08-26-getting-started/">starting with R + RStudio + Git</a>',
  ' ',

 "9.2.24", '<a href="posts/2024-09-04-dataviz/">data viz</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 1</a> - due 9.3',

 "9.9.24", '<a href="posts/2024-09-09-wrangling/">wrangling</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 2</a> - due 9.10 <br> Quiz 9.11',

   "9.16.24", '<a href="posts/2024-09-09-wrangling/">wrangling</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 3</a> - due 9.17',

   "9.23.24", '<a href="posts/2024-09-23-simulating/">simulating</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 4</a> - due 9.24 <br> Quiz 9.25',

  "9.30.24", '<a href="">permutation tests</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 5</a> - due 10.1',

  "10.7.24", '<a href="">bootstrapping</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 6</a> - due 10.8 <br> Quiz 10.9',

  "10.14.24", '<a href="">recipes</a>',
  ' ',
 
  '<font color = "#114B5F"><b>10.16.24</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><b>Initial Project Proposal due</b></font></a>', ' ',

 
 "10.21.24", '<a href="">knn + trees</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 7</a> - due 10.22 <br> Quiz 10.23',


  "10.28.24", '<a href="">bagging + RF</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 8</a> - due 10.29',

   '<font color = "#114B5F"><b>10.30.24</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><b>Final Project Proposal due</b></font></a>', ' ',

 "11.4.24", '<a href="">support vector machines</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 9</a> - due 11.5 <br> Quiz 11.6',

"11.11.24", '<a href="">clustering</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 10</a> - due 11.12',

  '<font color = "#114B5F"><b>11.13.24</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><b>Project Update</b></font></a>', ' ',

"11.18.24", '<a href="">clustering</a>',
  '<i class="fas fa-code"></i> <a href="https://github.com/orgs/ST47S-CompStats-Fall2024/repositories" target = "_blank">HW 11</a> - due 11.19 <br> Quiz 11.20',

 "11.25.24", '<a href="">Latent Dirichlet allocation</a>',
  ' ',

  '<font color = "#114B5F"><b>12.2.24</b></font>', '<font color = "#114B5F"><b>Data-ing in the World</b></font>', ' ',

 "12.2.24", '<a href="">fantastic extensions</a>',
  ' ',

 '<font color = "#114B5F"><b>12.6 + 12.24</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><b>Group Presentations</b></font></a>', ' ',

  '<font color = "#114B5F"><b>12.12.24</b></font>', '<a href = "https://m154-comp-stats.netlify.app/project.html"><font color = "#114B5F"><b>Final write-up</b></font></a>', ' ')
```


```{r}
#| echo: false
#| column: page
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(date ~ pct(20),
                 everything() ~ pct(40))
```



