---
title: "Simulating"
author: "Jo Hardin"
subtitle: "September 23 + 25, 2024"
format: 
  revealjs:
    incremental: false
    scrollable: true
    slide-number: true
    show-slide-number: all
    embed-resources: true
    multiplex: true
execute:
  echo: true
  warning: false
  message: false
bibliography: 
  - ../slides.bib
--- 


```{r include=FALSE}
library(tidyverse)
library(knitr)
library(lubridate)
library(openintro)
```


# Agenda  9/23/24

1. Why simulate?
2. What makes a good simulation?
3. Examples


## Goals of Simulating Complicated Models

The goal of simulating a complicated model is not only to create a program which will provide the desired results.  We also hope to be able to write code such that:

1. The problem is broken down into small pieces.
2. The problem has checks in it to see what works (run the lines *inside* the functions!).
3. uses simple code (as often as possible).


## Aside: a few R functions (`ifelse()`)
```{r}
data.frame(value = c(-2:2)) %>%
  mutate(abs_value = ifelse(value >=0, value, -value))  # abs val
```


## Aside: a few R functions (`case_when()`)
```{r}
set.seed(4747)
diamonds %>% select(carat, cut, color, price) %>%
  sample_n(20) %>%
  mutate(price_cat = case_when(
    price > 10000 ~ "expensive",
    price > 1500 ~ "medium", 
    TRUE ~ "inexpensive"))
```

## Aside: a few R functions (`sample()`)

*sampling*, *shuffling*,  and *resampling*: `sample()` 

```{r}
set.seed(47)
alph <- letters[1:10]
alph

sample(alph, 5, replace = FALSE) # sample (from a population)

sample(alph, 5, replace = TRUE) # sample (from a population)

sample(alph, 10, replace = FALSE)  # shuffle

sample(alph, 10, replace = TRUE)  # resample
```

## Why?

Three simulating methods are used for different purposes:

1. Monte Carlo methods - use repeated *sampling* from a **population** with known characteristics.


2. Randomization / Permutation methods - use *shuffling* (sampling without replacement from a **sample**) to test hypotheses of "no effect".


3. Bootstrap methods - use *resampling* (sampling with replacement from a **sample**) to establish confidence intervals.

## Aside: a few R functions (`set.seed()`)

What if we want to be able to generate the **same** random numbers (here on the interval from 0 to 1) over and over?

```{r}
set.seed(4747)
runif(4, 0, 1) # random uniform numbers

set.seed(123)
runif(4, 0, 1) # random uniform numbers

set.seed(4747)
runif(4, 0, 1) # random uniform numbers
```



# Small simulation example

```{=html}
<style>
.semi-transparent {
  opacity: 0.5;
}
</style>
```


* Simulation as easier than calculus for estimating probabilities.
* [Simulation to understand complicated models.]{.semi-transparent}
* [Simulation to consider methods with fewer assumptions.]{.semi-transparent}

## Sally & Joan

Consider a situation where Sally and Joan plan to meet to study in their college campus center [@mosteller1987;@MDSR]. They are both impatient people who will wait only 10 minutes for the other before leaving.

But their planning was incomplete. Sally said, "Meet me between 7 and 8 tonight at the student center." When should Joan plan to arrive at the campus center? And what is the probability that they actually meet?

## Simulate their meeting

Assume that Sally and Joan are both equally likely to arrive at the campus center anywhere between 7pm and 8pm. 

::: {.panel-tabset}

## vectorized 

```{r}
library(tictoc)
n <- 10000

tic()
meet_vect <- tibble(
  sally = runif(n, 0, max = 60),
  joan = runif(n, min = 0, max = 60),
  result = ifelse(
    abs(sally - joan) <= 10, "They meet", "They do not"
  )
)
toc()
```
## function

```{r}

meet_func <- function(nada){
  tibble(
    sally = runif(1, min = 0, max = 60),
    joan = runif(1, min = 0, max = 60),
    result = ifelse(
    abs(sally - joan) <= 10, "They meet", "They do not"
  )
  )
}
```


## `map()`

```{r}
tic()
meet_map <- 1:n |> 
  map(meet_func) |> 
  list_rbind()
toc()
```

## `for()` loop

```{r}
tic()
meet_for <- data.frame()
for(i in 1:n){
  meet_for <- meet_for |> rbind(
    tibble(
      sally = runif(1, min = 0, max = 60),
      joan = runif(1, min = 0, max = 60),
      result = ifelse(
    abs(sally - joan) <= 10, "They meet", "They do not"
  )))
}
toc()

```

:::


##  Results

The results themselves are equivalent.  Differing values due to randomness in the simulation.

::: {.panel-tabset}

## vectorized

```{r}
meet_vect |> 
  group_by(result) |> 
  summarize(number = n()) |> 
  mutate(proprotion = number / sum(number))
```

## `map()`

```{r}

meet_map |> 
  group_by(result) |> 
  summarize(number = n())|> 
  mutate(proprotion = number / sum(number))
```

## `for()` loop

```{r}
meet_for |> 
  group_by(result) |> 
  summarize(number = n())|> 
  mutate(proprotion = number / sum(number))
```

:::

## Visualizing the meet up


```{r}
meet_map |> 
  ggplot(aes(x = joan, y = sally, color = result)) +
  geom_point(alpha = 0.3) + 
  geom_abline(intercept = 10, slope = 1) + 
  geom_abline(intercept = -10, slope = 1) + 
  scale_color_brewer(palette = "Paired")
```


## Simulation best practices

* no magic numbers
* comment your code
* use informative names
* set a seed for reproducibility


# Bigger simulation example

## Thoughts on simulating

* break down the problem into **small** steps
* check to see what works
* simple is better

## Roulette

* A roulette wheel has 38 slots numbered 00, 0, and 1–36.
Two are green, 18 are red, and 18 are black.
* If a gambler bets based on color, the return on a $1 bet
is $2
* A gambler has $50, and will continuously bet $1 on red
until they double their money (have $100) or lose the
money they came with
* What is the probability the gambler doubles their money?

Question: Without calculating probabilities, how could you
design an experiment to estimate this probability?

## Design the simulation

Step 1: Need a Roulette wheel!  ... and money
Step 2: Will spin the wheel
Step 3: Depending on the wheel, update the money.
    - if spin is red: `money + 1`
    - if spin is not red: `money - 1`
Step 4: Keep spinning until `money = 100` or `money = 0`
Step 5: Repeat many times

## Step 1: create a roulette wheel

```{r}
wheel <- c(rep("green", 2), rep("black", 18), rep("red", 18))

wheel
```


* `rep()` repeats a value the specified number of times
* `c()` combines vectors (or scalars) into a single vector

## Step 2: spin the wheel

```{r}
spin <- sample(wheel, size = 1)

spin
```

## Step 3: update the money

```{r}
money <- 50

spin <- sample(wheel, size = 1)
money <- ifelse(spin == "red", money + 1, money  - 1)

spin
money
```

## Step 4: keep spinning (function first)

```{r}
spin_func <- function(money=20, i){
  wheel <- c(rep("green", 2), rep("black", 18), rep("red", 18))
  spin <- sample(wheel, size = 1)
  money <- ifelse(spin == "red", money + 1, money  - 1)
  money
}

spin_func(10)
spin_func(spin_func(10))
```

## Step 4: run multiple times

```{r}
set.seed(4747)
1:20 |> accumulate(spin_func, .init = 50)
set.seed(4747)
1:20 |> reduce(spin_func, .init = 50)
```

## Step 4: another function

```{r}
game_func <- function(rep, money, iter){
  data.frame(interim_money = 1:iter |> accumulate(spin_func, .init = money),
             game = 0:iter,
             rep = rep)
}

game_func(1, 20, 3)
```


## Step 5: Repeat many times

Note that map 

```{r}
1:20 |> map(game_func, money = 20, iter = 10) |> 
  list_rbind()
```





## References


